I wish to express my most sincere gratitude and appreciation to Professor Shan Zhao for his guidance, patience, and encouragement. Without his help, it would have been difficult for me to be focused in the right direction with all the patience and perseverance necessary before scholarly success. He has always been by my side as a local guardian, and it meant a lot to me.  His funding from the NSF grant DMS-1812930 titled "{\it A regularized Poisson Boltzmann model for fast computation of the ensemble average polar solvation energy}" was also a great support for the last part of my Ph. D. program. 

I would also like to express my gratitude toward my committee members for their time and support: the external member from the Department of Aerospace Engineering and Mechanics at the University of Alabama, Dr. Muhammad Ali Rob Sharif and the local members from the Department of Mathematics at the University of Alabama, Dr. Brendan Ames, Dr. Mojdeh Rasoulzadeh and Professor David Halpern. I want to especially thank Professor Halpern for his help and guidance to get my access to the High-Performance Computing facility from UAHPC and to introduce me to the Summer School at the MSRI, UC Berkeley. I wish to express my indebtedness to Professor David Cruz-Uribe for his continuous support to arrange travel funds from the Graduate School, and the College of Arts and Sciences. 

I want to take this occasion to thank Dr. Weihua Geng from the Southern Methodist University, and Professor Emil Alexov from Clemson University for their help and support for my research projects on different occasions. Besides Professor Zhao, Dr. Geng is the second most important person who helped and guided me to explore different areas on my research topic. 

I also want to recognize Khanh Dinh, David Neal, Xuan He, Timothy Homan and Summer Atkins for their friendship. Tania Hazra, Arum lee, Siwen Wang, and Hongsong Feng were more than just group mates and always helpful. My former roommate and a graduate student in the Department of Mechanical Engineering at UA, Md Abu Horaira Banna helped me to start using UAHPC which was an important skill to complete a significant portion of the Numerical Validations for the proposed methods in this dissertation. 

Finally, I want to thank my family for supporting me mentally through this program. My parents were always there to encourage and support my early mathematics education. I am grateful for all the emotional support I received from my wife Elizabeth Brezovich, and a lot of encouragement from her father, Professor Ivan Brezovich. 
